Summary of “An Investigation into Android In-App Ad Practice: Implications for App Developers” \\

### 2019-04-24 Conference Paper/Paper_Summary.tex
Final Update
Final version for Grading

The remainder of this paper proceeds as follows: Section \ref{SectionTwo} presents related work and Section \ref{SectionThree} provides relevant background in Android third-party ads. Section \ref{SectionFour} offers a detailed analysis of MAdLens system as well as a succinct discussion of the methodology used by this system. Section \ref{SectionFive} communicates the results of the large-scale measurements and gives implications based on statistical observation. Section \ref{SectionSix} discusses the limitations and future work of the reference paper, while Section \ref{SectionSeven} concludes this writing.

@@

As its name suggests, Popup type displays a pop-up window in front of the app’s GUI. Popups can be different forms or sizes and they can even take up the full screen if necessary. Although this type of ad could be unpleasant to the user, the study describes its Aggressiveness as Low. Even though Popups may be invasive and interrupt the app’s behavior, they can be easily closed by the user.

@@

\section{Proposed Scheme}
\label{SectionFour}
\begin{figure}[htbp]
	\includegraphics[width=0.5\textwidth,height=0.5\textheight,keepaspectratio]{system.png}
	\caption{Overview of MAdLens}
	\label{fig:system}
\end{figure}
The authors created MAdLens system (Fig. \ref{fig:system} ) which can identify internal third-party ad network modules from an Android app, map APIs of ad networks to specific ad types, and generate a detailed report of all the ad information for each app using static analysis techniques. Part of this system is a crawler that randomly picks applications from Google Play to create the Android App Dataset. For each application in the dataset, MAdLens automatically distinguishes all existing ad networks and then, using the API Mapping created based on Ad network SDK Documentation, classifies the present APIs in one of the five categories defined by the authors and generates an appropriate summary. To extract the relevant information from the applications, the system considers the fact that ads can be implemented either in the resource file (XML) or in Java code. For resources files, they decompile the apk file with Androidguard to get all the Android layout files, then parse all the XML to find the ads. Similarly, for Java code, the smali code is generated by Androguard after decompiling the apk file and ads are recognized in the smali text.

\section{Data Analysis and Results}
\label{SectionFive}
The research paper revealed multiple useful discoveries regarding mobile ads for Android applications. Developers may want to pay attention to the different implications that the authors have concluded after conducting a large-scale measurement study. There are 8 crucial implications which arose during the analysis:
\begin{itemize}
\item Due to the rise of different ad networks, developers have many different choices when it comes to determining ad placement in their apps. However, most developers take a more conservative approach when it comes to ads: 71\% of apps contain at most one ad library.
\item When it comes to choosing Ad types, programmers tend to choose Low-Aggressive ad types: Embedded and Popup. They are present in more than half of the analyzed apps. In contrast, the most aggressive types of Ads, Offerwall and Notification, are the least used ad types.
\item The number of Ads in an app is directly correlated with the type of category that app belongs to. The research paper affirms that business or utility apps are much less likely to have ads compared to apps that fall into the category of entertainment or casual.
\item According to the percentage of apps accommodating at least three types of ads, the research paper concludes that the two slightly aggressive ad types, Embedded and Popup, are the most popular among all the different categories. Although Offerwall is the most aggressive type of ad, it is relatively popular. The paper suggests that developers should consider using these three main ad types in their apps to increase their profits.
\item When determining how many different ad libraries to implement in an Android app, a developer should avoid including too many. According to the statistics provided by this research, empirically no more than 6 ad Networks should be added into an app to avoid bad ratings.
\item Developers should take into account the different stages of the app's life cycles when deciding how many ad networks to implement in their apps. When the app is at its initial stage, developers should use at most one ad network. They should use more when the app becomes more popular.
\item The authors propose that developers should opt to mainly use Embedded and Popup ads during any stage of the app's life cycle. Aggressive ad types should be used when their application becomes more mature.
\item Even though the previous implications may suggest that developers should stick to Low-Aggressiveness ads, after analyzing the Aggressiveness of the ads hosted by various applications, the research paper concludes a different idea. Developers can use both Low and High Aggressiveness ads at the same time to maximize their revenue. However, this practice should be carefully implemented and thoughtfully monitored.
\end{itemize}
\section{Limitations and Future Work}
\label{SectionSix}
MAdLens takes the static approach of analyzing and extracting the APIs from Android applications. Therefore, it has the inherited limitations of static analysis. The system counts the number of occurrences of various APIs at a specific time and because of the code control flow, some portions of the code are not necessarily executed. Thus, investigated apps could have had additional ads which were not captured by the system because they were not displayed when the experiment was conducted. There are dynamic approaches which can inspect an app’s run-time behavior, but these are still very challenging to implement at a large scale. A viable alternative proposed in the paper was a dynamic solution based on image recognition techniques to identify ad activities on the user interface. However, this option was left by the authors for future work as it required significant additional research.

\section{Conclusion}
\label{SectionSeven}
The analyzed paper represents one major step forward for the in-app advertising industry. It manages to fill in a gap caused by the lack of theoretical knowledge by providing insights for developers about how to optimize their app monetization with optimal ad placement choices. The authors collected 277,616 Android apps belonging to more than 48 categories and performed a comprehensive exploration before coming up with valuable results. These findings are able guide any mobile app programmer into Android in-app ad best practice.

>>>>

The remainder of this paper proceeds as follows: Section \ref{SectionTwo} presents related work and Section \ref{SectionThree} provides relevant background in Android third-party ads and a presentation of the system model. Section \ref{SectionFour} offers an analysis of the proposed scheme as well as a succinct discussion of the methodology used by this MAdLens. Section \ref{SectionFive} communicates the results of the large-scale measurements and gives implications based on statistical observations. Section \ref{SectionSix} discusses the limitations and future work of the reference paper, while Section \ref{SectionSeven} concludes this writing.

@@

As its name suggests, Popup type displays a pop-up window in front of the app’s GUI. Popups can take different forms or sizes and they can even take up the full screen if necessary. Although this type of ad could be unpleasant to the user, the study describes its Aggressiveness as Low. Even though Popups may be invasive and interrupt the app’s behavior, they can be easily closed by the user.

@@

\section{Proposed Scheme}
\label{SectionFour}
\begin{figure}[htbp]
	\includegraphics[width=0.5\textwidth,height=0.5\textheight,keepaspectratio]{system.png}
	\caption{Overview of MAdLens}
	\label{fig:system}
\end{figure}
The authors created MAdLens system (Fig. \ref{fig:system}) which can identify internal third-party ad network modules from an Android app, map APIs of ad networks to specific ad types, and generate a detailed report of all the ad information for each app using static analysis techniques. Part of this system is a crawler that randomly picks applications from Google Play to create the Android App Dataset. For each application in the dataset, MAdLens automatically distinguishes all existing ad networks and then, using the API Mapping created based on Ad network SDK Documentation, classifies the present APIs in one of the five categories defined by the authors and generates an appropriate summary. To extract the relevant information from the applications, the system considers the fact that ads can be implemented either in the resource file (XML) or in Java code. For resources files, they decompile the apk file with Androidguard to get all the Android layout files, then parse all the XML to find the ads. Similarly, for Java code, the smali code is generated by Androguard after decompiling the apk file and ads are recognized in the smali text.

\section{Data Analysis and Results}
\label{SectionFive}
The research paper revealed multiple useful discoveries regarding mobile ads for Android applications. Developers may want to pay attention to the different implications that the authors have concluded after conducting a large-scale measurement study. There are 8 crucial implications which arose during the analysis:
\begin{itemize}
\item Due to the rise of different ad networks, developers have many different choices when it comes to determining ad placement in their apps. However, most developers take a more conservative approach when it comes to ads: 71\% of apps contain at most one ad library.
\item When it comes to choosing Ad types, programmers tend to choose two Low-Aggressive ad types: Embedded and Popup. They are present in more than half of the analyzed apps. In contrast, the most aggressive types of Ads, Offerwall and Notification, are the least used ad types.
\item The number of Ads in an app is directly correlated with the type of category that app belongs to. The research paper affirms that business or utility apps are much less likely to have ads compared to apps that fall into the category of entertainment or casual.
\item According to the percentage of apps accommodating at least three types of ads, the research paper concludes that the two slightly aggressive ad types, Embedded and Popup, are the most popular among all the different categories. Although Offerwall is the most aggressive type of ad, it is relatively popular. The paper suggests that developers should consider using these three main ad types in their apps to increase their profits.
\item When determining how many different ad libraries to implement in an Android app, a developer should avoid including too many. According to the statistics provided by this research, empirically no more than 6 ad networks should be added into an app to avoid bad ratings.
\item Developers should take into account the different stages of the app's life cycles when deciding how many ad networks to implement in their apps. When the app is at its initial stage, developers should use at most one ad network. They can use more when the app becomes more popular.
\item The authors propose that developers should mainly use Embedded and Popup ads during any stage of the app's life cycle. Aggressive ad types could eventually be used when application becomes more mature.
\item Even though the previous implications may suggest that developers should stick to Low-Aggressiveness ads, after analyzing the Aggressiveness of the ads hosted by various applications, the research paper concludes a different idea. Developers can use both Low and High Aggressiveness ads at the same time to maximize their revenues. However, this practice should be carefully implemented and thoughtfully monitored.
\end{itemize}
\section{Limitations and Future Work}
\label{SectionSix}
MAdLens takes the static approach of analyzing and extracting the APIs from Android applications. Therefore, it has the inherited limitations of static analysis. The system counts the number of occurrences of various APIs at a specific time and because of the code control flow, some portions of the code are not necessarily executed. Thus, investigated apps could have had additional ads which were not captured by the system because they were not displayed when the experiment was conducted. There are dynamic approaches which can inspect an app’s run-time behavior, but these are still very challenging to implement at a large scale. A viable alternative proposed in the paper was a dynamic solution based on image recognition techniques to identify ad activities on the user interface. However, this option was left by the authors for future work as it required significant additional research.

\section{Conclusion}
\label{SectionSeven}
The analyzed paper represents one major step forward for the in-app advertising industry. It manages to fill in a gap caused by the lack of theoretical knowledge by providing insights for developers about how to optimize their app monetization with optimal ad placement choices. The authors collected 277,616 Android apps belonging to more than 48 categories and performed a comprehensive exploration before coming up with valuable results. These findings are able guide any mobile app programmer into Android advertisement best practice.
